Supplementary Information

### 2020-08-27 doc/manuscript/MEE_manuscript_SI.Rmd
worked on SI tables
#73 , #72

\newpage
## Table S2. Species analyzed, their characteristics, and bark allometries applied
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/species.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S2, format = "latex", booktabs = TRUE,  escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
*Bark allometry field indicates the species and site sampled to construct the bark allometry. When neither raw data nor an allometric equation for the study species was available, we selected the most appropriate equation that could be located for similar species. Equations are given in Table S4.

@@

## Table S3. Sampling details for species by site

>>>>

\newpage
## Table S2. Species analyzed, their characteristics, and bark allometries applied
(**[ISSUE #72 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/72)
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/species.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S2, format = "latex", booktabs = TRUE,  escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
*Bark allometry field indicates the species and site sampled to construct the bark allometry. When neither raw data nor an allometric equation for the study species was available, we selected the most appropriate equation that could be located for similar species. Equations are given in Table S4.

@@

## Table S3. Sampling details for species by site
(**[ISSUE #73 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/73)
